\newlist{biblist}{itemize}{1}
\setlist[biblist]{label={},left=0pt,itemindent=0pt,itemsep=0.5em}

\section*{References}
\begin{biblist}

\item Abdu, R., Müller, C., Kirfel, L., \& Dackermann, T. (2025). Demonstrating understanding of proportionality through embodied interaction: Eye–hand coordination as evidence. \emph{ZDM–Mathematics Education, 57}(1), 89–106.

\item Boaler, J. (1998). Open and closed mathematics: Student experiences and understandings. \emph{Journal for Research in Mathematics Education, 29}(1), 41–62.

\item D'Mello, S., \& Graesser, A. (2012). Dynamics of affective states during complex learning. \emph{Learning and Instruction, 22}(2), 145–157.

\item Edwards, M., Yang, Z., \& Lopez-Gonzalez, C. (2024). Fostering culturally-responsive calculus instruction. \emph{Ohio Journal of School Mathematics, 95}(1), 39--47. https://doi.org/10.18061/ojsm.4181

\item Fried, M. N. (2001). Can mathematics education and history of mathematics coexist? \emph{Science \& Education, 10}(4), 391–408.

\item Gay, G. (2010). \emph{Culturally responsive teaching: Theory, research, and practice} (2nd ed.). Teachers College Press.

\item Geertz, C. (1973). Thick description: Toward an interpretive theory of culture. In \emph{The interpretation of cultures} (pp. 3–30). Basic Books.

\item Holmes, W., \& Bialik, M. (2023). Artificial intelligence in education: Promises and implications for teaching and learning. \emph{OECD Education Working Papers, No. 270}. OECD Publishing.

\item Jahnke, H. N. (2000). The use of historical texts in mathematics education. \emph{Educational Studies in Mathematics, 41}(1), 63–87.

\item Pirie, S., \& Kieren, T. (1989). A recursive theory of mathematical understanding. \emph{For the Learning of Mathematics, 9}(3), 7–11.

\item Rexhepi, J., \& Makasevska, A. (2024). Impact of folding back instruction on third graders’ fraction understanding. \emph{Educational Studies in Mathematics, 115}(3), 483–502.

\item Ryan, R. M., \& Deci, E. L. (2000). Self-determination theory and the facilitation of intrinsic motivation, social development, and well-being. \emph{American Psychologist, 55}(1), 68–78.

\item Schoenfeld, A. H. (2004). The math wars. \emph{Educational Policy, 18}(1), 253–286.

\item Sfard, A. (1991). On the dual nature of mathematical conceptions: Reflections on processes and objects as different sides of the same coin. \emph{Educational Studies in Mathematics, 22}(1), 1–36.

\item Tall, D., \& Vinner, S. (1981). Concept image and concept definition in mathematics with particular reference to limits and continuity. \emph{Educational Studies in Mathematics, 12}(2), 151–169.

\item Thompson, A. G. (1994). Teachers’ beliefs and conceptions: A synthesis of the research. In D. A. Grouws (Ed.), \emph{Handbook of Research on Mathematics Teaching and Learning} (pp. 127–146). Macmillan.

\item Torrance, M., Lin, Y., \& Zhang, K. (2023). Artificial intelligence in STEM classrooms: Current practices and future possibilities. \emph{Journal of STEM Education, 24}(1), 13–28.

\item Vygotsky, L. S. (1978). \emph{Mind in society: The development of higher psychological processes}. Harvard University Press.

\item Wang, T. (2013). Big data needs thick data. \emph{Ethnography Matters}. \url{https://ethnographymatters.net/blog/2013/05/13/big-data-needs-thick-data/}

\item Wanzer, M. B., Frymier, A. B., \& Irwin, J. (2010). An explanation of the relationship between instructor humor and student learning: Instructional humor processing theory. \emph{Communication Education, 59}(1), 1–18.

\item Zepeda, C. D., Richey, J. E., Ronevich, P., \& Nokes-Malach, T. J. (2015). Direct instruction of metacognition benefits adolescent science learning, transfer, and motivation: An in vivo study. \emph{Journal of Educational Psychology, 107}(4), 954–970.

\item Zhai, X., Chu, H. E., \& Wang, J. (2023). Current trends and challenges in AI-based mathematics education. \emph{International Journal of Artificial Intelligence in Education, 33}(2), 345–366.

\end{biblist}
